Insert the article title here

### 2018-08-21 writeup/manuscript.tex
Fixig correlation graph

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed `super-foragers' showed no switch cost. This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. From a re-analysis of these data, we can estimate that test-retest reliability is <INSERT DETAILS>

@@

>>>>

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed `super-foragers' showed no switch cost. This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. From a re-analysis of these data, we can estimate that test-retest reliability for the mean lengths of runs is $r\approx 0.88$.

@@

The feature search condition from the MCFT will be discarded from this analysis, as the individual differences of interest relate to how people search in the conjunction condition. Measures for thr SHLS task will be taken from
